---
title: "Linear Mixed Effects Models for Kin & Speed Predictors for EEG"
author: "Jacob Salminen"
date: \`r format(Sys.Date(),"%d-%m-%Y")`\
output:
  html_document:
    theme: flatly
    toc: true
    toc_depth: 6
    toc_float:
      collapsed: true
      smooth_scroll: true
    df_print: paged
    self_contained: yes
---

```{r setup, include=FALSE}
# ERROR. png() device not found bug try: dev.off()
# ERROR. png() device not found fixed by changing cell names to a simple "windows friendlY" format so that knitr could save files.
knitr::opts_chunk$set(echo = TRUE)
```

# Packages & Setup
```{r}
# install.packages(c("tidyverse","purrr","R.matlab","readxl","dplyr"))
#%% PACKAGES FOR STATS
library(readxl);
library(purrr);
library(tidyverse);
library(tibble);
library(knitr);
library(kableExtra);
library(lme4);
library(MuMIn);
library(car);
library(effectsize)
library(sjPlot);
library(emmeans);
#%% PACKAGES FOR PLOTS & HTML HANDLING
# library(effects);
# library(sjPlot);
# library(plotly);
# library(webshot)
# library(reshape2);
# library(htmltools)
# library(Polychrome);
# library(htmlwidgets);
# library(shiny)
# library(webshot)
library(gtsummary);
library(gt)
library(scatterplot3d)
library(RColorBrewer)
library(openxlsx)
library(kableExtra) # devtools::install_github("haozhu233/kableExtra")
```

## GTSUMMARY THEME
``` {r options}
#%% ANOVA OPTIONS
options(contrasts = c("contr.sum","contr.poly")) # suggested for type III

#%% FIGURE & TABLE OPTIONS
gtsummary::set_gtsummary_theme(theme_gtsummary_journal("jama"))
#--
ispc <- function() {
  sys_name <- Sys.info()["sysname"]
  if (sys_name == "Windows") {
    return(TRUE)
  } else {
    return(FALSE)
  }
}
```
# Set Parameters 
```{r params} 
#%% CLUSTERS TO PLOT
clusters = c(3,4,5,6,7,8,9,10,11,12,13) # RSup/RSM, PreC, LSM, Mid Cing, LSup, LPPA, RPPA

#%% KIN PARAMS
#--
kin_measures = c('std_ml_exc_mm_gc','std_step_dur',
                 'mu_ml_exc_mm_gc','mu_step_dur');
kin_title_chars = c("ML Exc. Std. Dev","Step Dur. Std. Dev",
                    "ML Exc. Mean","Step Dur. Mean")

#%% EEG PARAMS
#--
eeg_measures = c('mu_avg_theta','mu_avg_alpha','mu_avg_beta',
                 'std_avg_theta','std_avg_alpha','std_avg_beta',
                 'cov_i_avg_theta','cov_i_avg_alpha','cov_i_avg_beta');
eeg_title_chars = c("**THETA** Mean","**ALPHA** Mean","**BETA** Mean",
                    "**THETA** Std. Dev.","**ALPHA** Std. Dev.","**BETA** Std. Dev.",
                    "**THETA** COVi","**ALPHA** COVi","**BETA** COVi");
```

# Load Data 
```{r loaddata}
#%% LOADING PARAMETERS
#-- close to final analysis pipelines
# fext = 'allcond_perstridefb_nfslidingb36'; # median for averaging across band for mu and covi
fext = 'allcond_perstridefb_mi_nfslidingb36'; # mean for averaging across band for mu and covi
#(03/31/2025) JS, changed STD to Standard error (normalizing over the number of strides included in the average)

#%% LOAD
excel_dir <- paste0("/jsalminen/GitHub/MIND_IN_MOTION_PRJ/_data/MIM_dataset/_studies/02202025_mim_yaoa_powpow0p3_crit_speed/__iclabel_cluster_allcond_rb3/icrej_5/11/kin_eeg_step_to_step/sbs_eeg_psd_kin_",fext,".xlsx")
fext = paste0(fext,"_rerun")

if(ispc()){
  excel_dir <- paste0("M:",excel_dir)
}else{
  excel_dir <- paste0("/blue/dferris",excel_dir);
}
orig_eegt <- read_excel(excel_dir,sheet="Sheet1")

#%% SUBSET
# orig_eegt <- orig_eegt %>%
#   select(subj_char,cond_char,speed_n,group_n,group_name,group_char,cluster_n,model_n,model_char,mu_stride_n,
#          std_avg_theta,std_avg_beta,std_avg_alpha,
#          std_ml_exc_mm_gc,std_ap_exc_mm_gc,std_ud_exc_mm_gc,
#          std_stance_dur,std_step_dur,std_single_sup_dur,std_double_sup_dur,
#          mu_avg_theta,mu_avg_beta,mu_avg_alpha,
#          cov_avg_theta,cov_avg_alpha,cov_avg_beta,
#          cov_i_avg_theta,cov_i_avg_alpha,cov_i_avg_beta,
#          qcv_i_avg_theta,qcv_i_avg_alpha,qcv_i_avg_beta,
#          mu_ml_exc_mm_gc,mu_ap_exc_mm_gc,mu_ud_exc_mm_gc,
#          mu_stance_dur,mu_step_dur,mu_single_sup_dur,mu_double_sup_dur,
#          );
orig_eegt <- transform(orig_eegt,cov_avg_theta_calc = log10((std_avg_theta/abs(mu_avg_theta))*100))
orig_eegt <- transform(orig_eegt,cov_avg_alpha_calc = log10((std_avg_alpha/abs(mu_avg_alpha))*100))
orig_eegt <- transform(orig_eegt,cov_avg_beta_calc = log10((std_avg_beta/abs(mu_avg_beta))*100))
orig_eegt <- transform(orig_eegt,cov_i_avg_theta = log10(cov_i_avg_theta))
orig_eegt <- transform(orig_eegt,cov_i_avg_alpha = log10(cov_i_avg_alpha))
orig_eegt <- transform(orig_eegt,cov_i_avg_beta = log10(cov_i_avg_beta))
orig_eegt <- transform(orig_eegt,qcv_i_avg_theta = log10(abs(qcv_i_avg_theta)))
orig_eegt <- transform(orig_eegt,qcv_i_avg_alpha = log10(abs(qcv_i_avg_alpha)))
orig_eegt <- transform(orig_eegt,qcv_i_avg_beta = log10(abs(qcv_i_avg_beta)))
#--
orig_eegt <- transform(orig_eegt,cov_ml_exc_mm_gc = 100*cov_ml_exc_mm_gc)
orig_eegt <- transform(orig_eegt,cov_step_dur = 100*cov_step_dur)
orig_eegt <- transform(orig_eegt,cov_stance_dur = 100*cov_stance_dur)

```

# Format Table
```{r}
eegt <- orig_eegt;

#%% SELECT SPEEDS
eegt <- filter_at(eegt,vars('cond_char'), any_vars(. %in% c('0p25','0p5','0p75','1p0')))
flat_speeds = unique(eegt$cond_char)

#%% MUTATE VARIABLES
eegt$speed_cond_num <- as.numeric(eegt$speed_n); #as.numeric(eegt$cond_char);
eegt <- mutate(eegt,across(c('subj_char'), factor))
eegt <- mutate(eegt,across(c('group_char'), factor))
eegt <- mutate(eegt,across(c('group_name'), factor))
eegt <- mutate(eegt,across(c('model_char'), factor))

#%% COLORS
color_pal_subj = brewer.pal(9,'PuBuGn')
color_pal_subj = color_pal_subj[5:9];

#%% TBL VALUES
tbl_clusterS = unique(eegt$cluster_n);
tbl_subjects = unique(eegt$subj_char);
tbl_groups = unique(eegt$group_char);

#%% DISPLAY TBL
head(eegt)
dtbl <- eegt;
rm(eegt)
```

# Table Manipulations
```{r tblmanip}
#%% SELECT VALUES
dtbl <- orig_eegt
dtbl <- dtbl %>%
  select(subj_char,cond_char,speed_n,group_char,cluster_n,model_n,
     std_avg_theta,std_avg_beta,std_avg_alpha,
     std_ml_exc_mm_gc,std_ap_exc_mm_gc,std_ud_exc_mm_gc,
     std_stance_dur,std_step_dur,std_single_sup_dur,std_double_sup_dur,
     mu_avg_theta,mu_avg_beta,mu_avg_alpha,
     cov_avg_theta_calc,cov_avg_alpha_calc,cov_avg_beta_calc,
     cov_i_avg_theta,cov_i_avg_alpha,cov_i_avg_beta,
     mu_ml_exc_mm_gc,mu_ap_exc_mm_gc,mu_ud_exc_mm_gc,
     mu_stance_dur,mu_step_dur,mu_single_sup_dur,mu_double_sup_dur,
     cov_ml_exc_mm_gc,cov_step_dur,cov_stance_dur,
     cov_avg_theta,cov_avg_alpha,cov_avg_beta);

#%% CREATE MEAN & STD MEASURES PER CONDITION
dtbl <- dtbl %>%
  group_by(subj_char,cond_char,speed_n,model_n,group_char,cluster_n) %>%
  summarise_all(list("mean","sd"))
dtbl <- transform(dtbl,cov_mu_avg_theta = log10(mu_avg_theta_fn2/abs(mu_avg_theta_fn1)))
dtbl <- transform(dtbl,cov_mu_avg_beta = log10(mu_avg_beta_fn2/abs(mu_avg_beta_fn1)))
dtbl <- transform(dtbl,cov_mu_avg_alpha = log10(mu_avg_alpha_fn2/abs(mu_avg_alpha_fn1)))
dtbl <- transform(dtbl,cov_std_avg_theta = std_avg_theta_fn2/abs(std_avg_theta_fn1))
dtbl <- transform(dtbl,cov_std_avg_beta = std_avg_beta_fn2/abs(std_avg_beta_fn1))
dtbl <- transform(dtbl,cov_std_avg_alpha = std_avg_alpha_fn2/abs(mu_avg_alpha_fn1))
dtbl <- transform(dtbl,cov_ml_exc = mu_ml_exc_mm_gc_fn2/abs(mu_ml_exc_mm_gc_fn1))
dtbl <- transform(dtbl,cov_step_dur = mu_step_dur_fn2/abs(mu_step_dur_fn1))
dtbl <- transform(dtbl,cov_stance_dur = mu_stance_dur_fn2/abs(mu_stance_dur_fn1))
#--
dtbl <- transform(dtbl,cov_avg_theta_fn1 = abs(cov_avg_theta_fn1));
dtbl <- transform(dtbl,cov_avg_alpha_fn1 = abs(cov_avg_alpha_fn1));
dtbl <- transform(dtbl,cov_avg_beta_fn1 = abs(cov_avg_beta_fn1));

#%% CHANGE GROUP LABS
dtbl <- dtbl %>%
  mutate(group_char = as.character(group_char),
         group_char = if_else(group_char == 'H1000', 'YA',group_char),
         group_char = if_else(group_char == 'H2000', 'OHFA',group_char),
         group_char = if_else(group_char == 'H3000', 'OLFA',group_char),
         group_char = as.factor(group_char))
#%% MUTATE VARIABLES
dtbl$speed_cond_num <- as.numeric(dtbl$speed_n); #as.numeric(dtbl$cond_char);
dtbl <- mutate(dtbl,across(c('subj_char'), factor))
dtbl <- mutate(dtbl,across(c('group_char'), factor))
dtbl <- mutate(dtbl,across(c('model_n'), factor))

color_pal_subj = brewer.pal(9,'PuBuGn')
color_pal_subj = color_pal_subj[5:9];

#%% TBL VALUES
tbl_clusterS = unique(dtbl$cluster_n);
tbl_subjects = unique(dtbl$subj_char);
tbl_groups = unique(dtbl$group_char);

#%% KIN PARAMS
# kin_measures = c('cov_ml_exc','cov_step_dur','cov_stance_dur');
# kin_title_chars = c("ml exc. COV","step dur. COV","stance dur. COV")
kin_measures = c('cov_ml_exc_mm_gc_fn1','cov_step_dur_fn1','cov_stance_dur_fn1');
kin_title_chars = c("ml exc. COV","step dur. COV","stance dur. COV")

#%% EEG PARAMS
#-- EEG PARAMS (fn1 = mean, fn2 = sd)
eeg_measures = c('std_avg_theta_fn1','std_avg_beta_fn1','std_avg_alpha_fn1',
                 'cov_i_avg_theta_fn1','cov_i_avg_beta_fn1','cov_i_avg_alpha_fn1',
                  'mu_avg_theta_fn1','mu_avg_beta_fn1','mu_avg_alpha_fn1');
eeg_title_chars = c("**THETA** STD","**BETA** STD","**ALPHA** STD",
                    "**THETA** COVi","**BETA** COVi","**ALPHA** COVi",
                      "**THETA** Mean","**BETA** Mean","**ALPHA** Mean");
#(03/31/2025) JS, COVi seems to me, the most practical. You take the mean/median within a the frequency band of the flattened PSD for each gait cycle then derive the COV for the N strides instead of taking the mean of the PSD across the strides then the mean within the band. I have to log scale the measure no matter what.

#-- CLUSTERS TO PLOT
clusters = c(3,4,5,6,7,8,9,10,11,12,13) # 02202025_mim_yaoa_powpow0p3_crit_speed

#%% MUTATE mn VARIABLES
fext = paste0("meansd_",fext);
dtbl$speed_cond_num <- as.numeric(dtbl$speed_n);
write.xlsx(dtbl,paste0("03312025_lme_eeg_kin_",fext,"_tbl.xlsx"))
```

# Functions
```{r}
calc_cohensf2 <- function(mod_main,mod_alt){
  r2_out = r.squaredGLMM(mod_main);
  r2_outalt = r.squaredGLMM(mod_alt);
  r2m = r2_out[1] # input your R2
  f2m = r2m/(1 - r2m)
  r2c = r2_out[2] # input your R2
  f2c = r2c/(1 - r2c)
  f2m = (r2_out[1]-r2_outalt[1])/(1-r2_out[1]);
  f2c = (r2_out[2]-r2_outalt[2])/(1-r2_out[2]);
  print(str_glue("r2m: {round(r2m,4)},\tr2c: {round(r2c,4)}\n\n"))
  print(str_glue("f2m: {round(f2m,4)},\tf2c: {round(f2c,4)}\n\n"))
  vals = data.frame(r2m, r2c, f2m, f2c);
  return (vals)
}

#%% EXCEL DATAFRAME
excel_df <- data.frame(cluster_num=double(),
                      group_char=character(),
                      model_char=character(),
                      kinematic_char=character(),
                      freq_band_char=character(),
                      mod_num_obs=character(),
                      coeff_chars=character(),
                      coeffs=character(),
                      confint_chars=character(),
                      emmeans=character(),
                      emmeans_se=character(),
                      confint_lwr=character(),
                      confint_upr=character(),
                      anv_chars=character(),
                      anv_pvals=character(),
                      anv_stats=character(),
                      anv_dfs=character(),
                      r2_m_int=double(),
                      r2_c_int=double(),
                      f2_m_int=double(),
                      f2_c_int=double(),
                      fsq_chars=character(),
                      fsq_vals=character(),
                      etasq_chars=character(),
                      etasq_vals=character(),
                      ran_effs_char=character(),
                      ran_effs_n=character())
```


# SPEED-GROUP INTERACTION) LME EEG ~ 1+speed+group+speed:group
```{r eegspeedgroupinter, echo=FALSE, message=FALSE, results="asis"}
theme_set(theme_classic()) # This sets the default ggplot theme
#%% LOOP VARS
cis <- rep(NA,length(clusters)*length(eeg_measures))
eis <- rep(NA,length(clusters)*length(eeg_measures))
cnt = 1;
for (i in 1:length(clusters)) {
  for(k in 1:length(eeg_measures)){
    cis[cnt] = i;
    eis[cnt] = k;
    cnt = cnt + 1;
  }
}

for (i in 1:length(cis)){
  #%% SET LOOP PARAMS
  ci = clusters[cis[i]];
  ei = eeg_measures[eis[i]];
  

  #%% HTML TAG
  cat(paste0("\n\n## ", ci,',',ei,"\n"))

  #%% SUBSET BY CLUSTER
  tmpt <- filter_at(dtbl,vars('cluster_n'), any_vars(. %in% ci));
  # -- remove NAN cases
  tmpt = tmpt[complete.cases(tmpt[[ei]]),];

  #%% THAT ARE GREATER THAN OR LESS THAN 3STD FROM MEAN
  #- mean & std cutoff
  # muc = mean(tmpt[[ei]])
  # stdc = sd(tmpt[[ei]])
  # inds_keep = tmpt[[ei]] > muc-3*stdc & tmpt[[ei]] < muc+3*stdc
  # tmpt = tmpt[inds_keep,]
  
  # inds_keep = tmpt[[ei]] < 500
  # tmpt = tmpt[inds_keep,]

  #%% COMPUTE LME MODEL
  mod_char = paste(ei," ~ 1 + speed_cond_num + group_char + speed_cond_num:group_char + (1|subj_char)");
  mod <- lme4::lmer(str_glue(mod_char), data=tmpt);
  tbl <- mod %>%
    tbl_regression(tidy_fun = broom.mixed::tidy,
                   pvalue_fun = purrr::partial(style_pvalue, digits = 2),
                   intercept=TRUE,
                   estimate_fun=function(x) style_sigfig(x,2),
                   conf.level=0.95,
                   ) %>%
    add_global_p() %>%
    bold_labels()

  #%% PRINT TABLE
  t_out <- as_gt(tbl) %>%
    gt::tab_header(title=c("Changes in ",ei,"for Cluster: ",ci)) %>%
    gt::tab_options(table.layout = "fixed") %>%
    gt::as_raw_html()
  print(t_out)
  #--
  t_out <- as_gt(tbl) %>%
    gt::tab_header(title=c("Changes in ",ei)) %>%
    gt::tab_options(table.layout = "fixed") %>%
    gt::as_word(align="center",
                caption_location="bottom",
                caption_align="left",
                split=FALSE,
                keep_with_next=TRUE)
  
  #%%
  
  #-- extract fixed & random effects coeffs
  anv_vals <- car::Anova(mod,type=3)
  fix_effs <- fixef(mod)
  ran_effs <- ranef(mod)$subj_char
  #-- calculate effect sizes using r-package
  anv_vals_f <- car::Anova(mod,type=3,test.statistic = "F")
  cohens_fsq_res <- effectsize::cohens_f_squared(anv_vals_f, partial = TRUE)
  #--
  tbl <- mod %>% 
    tbl_regression(tidy_fun=purrr::partial(broom.mixed::tidy,effects='fixed'),
                   pvalue_fun=purrr::partial(style_pvalue, digits = 2),
                   intercept=TRUE,
                   estimate_fun=function(x) style_sigfig(x,2),
                   conf.level=0.95,
                   add_reference_rows=TRUE,
                   add_pairwise_contrasts=TRUE,
                   pairwise_variables=c('group_char'),
                   emmeans_args=list(spec=c('speed_cond_num','group_char'),level=0.95),
                   contrasts_adjust="fdr",
                   add_header_rows=TRUE,
                   interaction_sep=":",
                   add_n=TRUE,
                   keep_model=TRUE,
                   label=list(group_char~"Age",
                              speed_cond_num~"Walking Speed"),
                   term_labels=c(group_char="Age Group",speed_cond_num="Speed")
                   )  %>%
    add_global_p() %>%
    add_glance_source_note(include=c(nobs,REMLcrit,logLik,df.residual)) %>%
    as_gt() %>%
    cols_add(ChiSq=anv_vals$Chisq)
  
  gt_adf = data.frame(anv_vals) %>%
    gt(rownames_to_stub = T) %>%
    tab_header(
      # title=c(eeg_title_chars[eis[i]]),
      subtitle="Descriptive Statistics"
    )
  d <- tbl |>
    summary_rows(
      data = gt_adf,
      columns=c("Df", "F.value", "Pr(>F)"),
      groups=c("speed_cond_num","group_char","speed_cond_num:group_char"),
      labeller = function(x) paste(x),  # Or whatever labeller you prefer
      fmt=function(x) style_sigfig(x,2)
    )
    
  
  
  #%% R-SQUARED VALUE
  # r.squaredGLMM() %>%
  #   print(str_glue("{outcome}\n R2m: {round(mod[1],4)},\tR2c: {round(mod[2],4)}\n\n"))

  #%% EFFECT SIZES
  cat(paste0("\n\n### model effect sizes\n"))
  #-- Intercept Model for Cohen's f^2
  print('intercept model\n');
  mod_char_int = paste(ei," ~ 1 + (1|subj_char)");
  tmp_mod = lme4::lmer(str_glue(mod_char_int), data=tmpt)
  cf_alt = calc_cohensf2(mod, tmp_mod)
  #-- calculate effect sizes using r-package
  anv_vals_f <- car::Anova(mod,type=3,test.statistic = "F")
  etasq_res <- effectsize::eta_squared(anv_vals_f, partial = TRUE)
  cohens_fsq_res <- effectsize::cohens_f_squared(anv_vals_f, partial = TRUE)
  #-- confidence intervals
  summ <- summary(mod);
  coeff_chars = row.names(summ$coefficients)
  confintvs <- data.frame(emmeans::emmeans(mod,spec=c('speed_cond_num','group_char'),level=0.95));
  emm = emmeans::emmeans(mod,spec=c('speed_cond_num','group_char'),level=0.95);
  bfc = emmeans::contrast(emm,adjutst="bonferroni")
  pwc = emmeans::contrast(emm,method = "pairwise")
  print(kable(anv_vals));
  print(kable(data.frame(bfc)));
  print(kable(data.frame(pwc)));
  print(kable(confintvs));

  #%% EXCEL PRINTS
  new_row = data.frame(cluster_num=ci,
                      group_char=c('all'),
                      model_char=c('speed_group_intact_all'),
                      kinematic_char=c('none'),
                      freq_band_char=c(ei),
                      mod_num_obs=nrow(tmpt),
                      coeff_chars=paste(unlist(coeff_chars),collapse=','),
                      coeffs=paste(unlist(mod@beta),collapse=','),
                      confint_chars=paste(unlist(confintvs$group_char),collapse=','),
                      emmeans=paste(unlist(as.numeric(confintvs$emmean)),collapse=','),
                      emmeans_se=paste(unlist(as.numeric(confintvs$SE)),collapse=','),
                      confint_lwr=paste(unlist(as.numeric(confintvs$lower.CL)),collapse=','),
                      confint_upr=paste(unlist(as.numeric(confintvs$upper.CL)),collapse=','),
                      anv_chars=paste(unlist(row.names(anv_vals)),collapse=','),
                      anv_pvals=paste(unlist(anv_vals$`Pr(>Chisq)`),collapse=','),
                      anv_stats=paste(unlist(anv_vals$Chisq),collapse=','),
                      anv_dfs=paste(unlist(anv_vals$Df),collapse=','),
                      r2_m_int=cf_alt$r2m,
                      r2_c_int=cf_alt$r2c,
                      f2_m_int=cf_alt$f2m,
                      f2_c_int=cf_alt$f2c,
                      fsq_chars=paste(unlist(cohens_fsq_res$Parameter),collapse=','),
                      fsq_vals=paste(unlist(cohens_fsq_res$Cohens_f2_partial),collapse=','),
                      etasq_chars=paste(unlist(etasq_res$Parameter),collapse=','),
                      etasq_vals=paste(unlist(etasq_res$Eta2_partial),collapse=','),
                      ran_effs_char=paste(unlist(row.names(ran_effs)),collapse=','),
                      ran_effs_n=paste(unlist(ran_effs$`(Intercept)`),collapse=','))
  excel_df <- rbind(excel_df,new_row)

  #%% MODEL VALIDATION PLOTS
  cat(paste0("\n\n### model validations\n"))
  print(plot_model(mod, type = 'diag'))
  cat("\n")

  #%% MODEL VALIDATIONS
  cat(paste0("\n\n### model validations\n"))
  # print(plot_model(mod, type = 'diag'))
  cat("\n")
  tmpt$fit.m <- predict(mod, re.form = NA)
  tmpt$fit.c <- predict(mod, re.form = NULL)

  #%% VISUALIZATION OF MODELS
  cat(paste0("\n\n### data plot\n"))
  theme_set(theme_classic()) # This sets the default ggplot theme
  print(
    tmpt %>%
      ggplot() +
      geom_jitter(aes(x = speed_cond_num, y = .data[[ei]], color = subj_char), pch=20, size=10, alpha=0.2) +
      geom_line(aes(x= speed_cond_num, y=fit.c, group = subj_char),linetype = "dashed", linewidth = .5) +
      geom_line(aes(x= speed_cond_num, y=fit.m), linewidth = 2)+
      facet_wrap(~group_char) +
      ggtitle(eeg_title_chars[eis[i]])+
      xlab("Treadmill Speed (m/s)") +
      ylab(eeg_title_chars[eis[i]]) +
      guides(group="none")
  # )

}
```

# SPEED-GROUP) LME EEG ~ 1+speed+group
```{r eegspeedgroup, echo=FALSE, message=FALSE, results="asis"}
theme_set(theme_classic()) # This sets the default ggplot theme
#%% LOOP VARS
cis <- rep(NA,length(clusters)*length(eeg_measures))
eis <- rep(NA,length(clusters)*length(eeg_measures))
cnt = 1;
for (i in 1:length(clusters)) {
  for(k in 1:length(eeg_measures)){
    cis[cnt] = i;
    eis[cnt] = k;
    cnt = cnt + 1;
  }
}

for (i in 1:length(cis)){
  #%% SET LOOP PARAMS
  ci = clusters[cis[i]];
  ei = eeg_measures[eis[i]];

  #%% HTML TAG
  cat(paste0("\n\n## ", ci,',',ei,"\n"))

  #%% SUBSET BY CLUSTER
  tmpt <- filter_at(dtbl,vars('cluster_n'), any_vars(. %in% ci));
  # -- remove NAN cases
  tmpt = tmpt[complete.cases(tmpt[[ei]]),];
  #(03/26/2025) JS, this is for the COV measures
  
  #%% THAT ARE GREATER THAN OR LESS THAN 3STD FROM MEAN
  #- mean & std cutoff
  # muc = mean(tmpt[[ei]])
  # stdc = sd(tmpt[[ei]])
  # inds_keep = tmpt[[ei]] > muc-3*stdc & tmpt[[ei]] < muc+3*stdc
  # tmpt = tmpt[inds_keep,]

  #%% COMPUTE LME MODEL
  mod_char = paste(ei," ~ 1 + speed_cond_num + group_char + (1|subj_char)");
  mod <- lme4::lmer(str_glue(mod_char), data=tmpt);
  tbl <- mod %>%
    tbl_regression(tidy_fun = broom.mixed::tidy,
                   pvalue_fun = purrr::partial(style_pvalue, digits = 2),
                     intercept=TRUE) %>%
    add_global_p() %>%
    add_q()

  #%% PRINT TABLE
  t_out <- as_gt(tbl) %>%
    gt::tab_header(title=c("Changes in ",ei,"for Cluster: ",ci)) %>%
    gt::tab_options(table.layout = "fixed") %>%
    gt::as_raw_html()
  print(t_out)
  #-- extract fixed & random effects coeffs
  anv_vals <- car::Anova(mod,type=3)
  fix_effs <- fixef(mod)
  ran_effs <- ranef(mod)$subj_char

  #%% R-SQUARED VALUE
  # r.squaredGLMM() %>%
  #   print(str_glue("{outcome}\n R2m: {round(mod[1],4)},\tR2c: {round(mod[2],4)}\n\n"))

  #%% EFFECT SIZES
  cat(paste0("\n\n### model effect sizes\n"))
  #-- Intercept Model for Cohen's f^2
  print('intercept model\n');
  mod_char_int = paste(ei," ~ 1 + (1|subj_char)");
  tmp_mod = lme4::lmer(str_glue(mod_char_int), data=tmpt)
  cf_alt = calc_cohensf2(mod, tmp_mod)
  #-- calculate effect sizes using r-package
  anv_vals_f <- car::Anova(mod,type=3,test.statistic = "F")
  etasq_res <- effectsize::eta_squared(anv_vals_f, partial = TRUE)
  cohens_fsq_res <- effectsize::cohens_f_squared(anv_vals_f, partial = TRUE)
  #-- confidence intervals
  summ <- summary(mod);
  coeff_chars = row.names(summ$coefficients)
  confintvs <- data.frame(emmeans::emmeans(mod,spec=c('speed_cond_num','group_char'),level=0.95))
  emm = emmeans::emmeans(mod,spec=c('speed_cond_num','group_char'),level=0.95);
  bfc = emmeans::contrast(emm,adjutst="bonferroni")
  pwc = emmeans::contrast(emm,method = "pairwise")
  print(kable(anv_vals));
  print(kable(data.frame(bfc)));
  print(kable(data.frame(pwc)));
  print(kable(confintvs));

  #%% EXCEL PRINTS
  new_row = data.frame(cluster_num=ci,
                      group_char=c('all'),
                      model_char=c('speed_group_all'),
                      kinematic_char=c('none'),
                      freq_band_char=c(ei),
                      mod_num_obs=nrow(tmpt),
                      coeff_chars=paste(unlist(coeff_chars),collapse=','),
                      coeffs=paste(unlist(mod@beta),collapse=','),
                      confint_chars=paste(unlist(confintvs$group_char),collapse=','),
                      emmeans=paste(unlist(as.numeric(confintvs$emmean)),collapse=','),
                      emmeans_se=paste(unlist(as.numeric(confintvs$SE)),collapse=','),
                      confint_lwr=paste(unlist(as.numeric(confintvs$lower.CL)),collapse=','),
                      confint_upr=paste(unlist(as.numeric(confintvs$upper.CL)),collapse=','),
                      anv_chars=paste(unlist(row.names(anv_vals)),collapse=','),
                      anv_pvals=paste(unlist(anv_vals$`Pr(>Chisq)`),collapse=','),
                      anv_stats=paste(unlist(anv_vals$Chisq),collapse=','),
                      anv_dfs=paste(unlist(anv_vals$Df),collapse=','),
                      r2_m_int=cf_alt$r2m,
                      r2_c_int=cf_alt$r2c,
                      f2_m_int=cf_alt$f2m,
                      f2_c_int=cf_alt$f2c,
                      fsq_chars=paste(unlist(cohens_fsq_res$Parameter),collapse=','),
                      fsq_vals=paste(unlist(cohens_fsq_res$Cohens_f2_partial),collapse=','),
                      etasq_chars=paste(unlist(etasq_res$Parameter),collapse=','),
                      etasq_vals=paste(unlist(etasq_res$Eta2_partial),collapse=','),
                      ran_effs_char=paste(unlist(row.names(ran_effs)),collapse=','),
                      ran_effs_n=paste(unlist(ran_effs$`(Intercept)`),collapse=','))
  excel_df <- rbind(excel_df,new_row)

  #%% MODEL VALIDATION PLOTS
  cat(paste0("\n\n### model validations\n"))
  print(plot_model(mod, type = 'diag'))
  cat("\n")

  #%% MODEL VALIDATIONS
  cat(paste0("\n\n### model validations\n"))
  # print(plot_model(mod, type = 'diag'))
  cat("\n")
  tmpt$fit.m <- predict(mod, re.form = NA)
  tmpt$fit.c <- predict(mod, re.form = NULL)

  #%% VISUALIZATION OF MODELS
  cat(paste0("\n\n### data plot\n"))
  theme_set(theme_classic()) # This sets the default ggplot theme
  print(
    tmpt %>%
      ggplot() +
      geom_jitter(aes(x = speed_cond_num, y = .data[[ei]], color = subj_char), pch=20, size=10, alpha=0.2) +
      geom_line(aes(x= speed_cond_num, y=fit.c, group = subj_char),linetype = "dashed", linewidth = .5) +
      geom_line(aes(x= speed_cond_num, y=fit.m), linewidth = 2)+
      facet_wrap(~group_char) +
      ggtitle(eeg_title_chars[eis[i]])+
      xlab("Treadmill Speed (m/s)") +
      ylab(eeg_title_chars[eis[i]]) +
      guides(group="none")
  )

}
# write.xlsx(excel_df,paste0("03122025_lme_eeg_kin_",fext,"_stats.xlsx"))
```

# KIN INTERACTION) LME Kin ~ 1+speed+group+speed:group
```{r speedkininterall, echo=FALSE, message=FALSE, results="asis"}
theme_set(theme_classic()) # This sets the default ggplot theme
#%% LOOP VARS
kis <- rep(NA,length(kin_measures))
cnt = 1;
for(j in 1:length(kin_measures)){
  kis[cnt] = j;
  cnt = cnt + 1;
}

for (i in 1:length(kis)){
  #%% SET LOOP PARAMS
  ki = kin_measures[kis[i]];

  #%% HTML TAG
  cat(paste0("\n\n## ", ki,"\n"))
  
  #%% CREATE MEAN & STD MEASURES PER CONDITION
  tmpt = dtbl;
  tmpt <- tmpt %>%
    group_by(subj_char,cond_char,speed_n,model_n,group_char) %>%
    summarise_all(list("mean"))
    
  #%% SAVE TABLE
  # write.xlsx(tmpt,paste0("03312025_lme_behav_kin_meansd_",fext,"_tbl.xlsx"))

  
  #%% SUBSET BY CLUSTER
  #-- remove NAN cases
  tmpt = tmpt[complete.cases(tmpt[[ki]]),];
  #(03/26/2025) JS, this is for the COV measures

  #%% COMPUTE LME MODEL
  mod_char = paste(ki," ~ 1 + speed_cond_num + group_char + speed_cond_num:group_char + (1|subj_char)");
  mod <- lme4::lmer(str_glue(mod_char), data=tmpt);
  tbl <- mod %>%
    tbl_regression(tidy_fun = broom.mixed::tidy,
                   pvalue_fun = purrr::partial(style_pvalue, digits = 2),
                     intercept=TRUE) %>%
    add_global_p() %>%
    add_q()

  #%% PRINT TABLE
  t_out <- as_gt(tbl) %>%
    gt::tab_header(title=c("Changes in ",ki)) %>%
    gt::tab_options(table.layout = "fixed") %>%
    gt::as_raw_html()
  print(t_out)
  #-- extract fixed & random effects coeffs
  anv_vals <- car::Anova(mod,type=3)
  fix_effs <- fixef(mod)
  ran_effs <- ranef(mod)$subj_char

  #%% R-SQUARED VALUE
  # r.squaredGLMM() %>%
  #   print(str_glue("{outcome}\n R2m: {round(mod[1],4)},\tR2c: {round(mod[2],4)}\n\n"))

  #%% EFFECT SIZES
  cat(paste0("\n\n### model effect sizes\n"))
  #-- Intercept Model for Cohen's f^2
  print('intercept model\n');
  mod_char_int = paste(ki," ~ 1 + (1|subj_char)");
  tmp_mod = lme4::lmer(str_glue(mod_char_int), data=tmpt)
  cf_alt = calc_cohensf2(mod, tmp_mod)
  #-- calculate effect sizes using r-package
  anv_vals_f <- car::Anova(mod,type=3,test.statistic = "F")
  etasq_res <- effectsize::eta_squared(anv_vals_f, partial = TRUE)
  cohens_fsq_res <- effectsize::cohens_f_squared(anv_vals_f, partial = TRUE)
  #-- confidence intervals
  summ <- summary(mod);
  coeff_chars = row.names(summ$coefficients)
  confintvs <- data.frame(emmeans::emmeans(mod,spec=c('speed_cond_num','group_char'),level=0.95))
  emm = emmeans::emmeans(mod,spec=c('speed_cond_num','group_char'),level=0.95);
  bfc = emmeans::contrast(emm,adjutst="bonferroni")
  pwc = emmeans::contrast(emm,method = "pairwise")
  print(kable(anv_vals));
  print(kable(data.frame(bfc)));
  print(kable(data.frame(pwc)));
  print(kable(confintvs));
  
  #%% EXCEL PRINTS
  new_row = data.frame(cluster_num=0,
                      group_char=c('all'),
                      model_char=c('speed_group_intact_all'),
                      kinematic_char=c(ki),
                      freq_band_char=c('none'),
                      mod_num_obs=nrow(tmpt),
                      coeff_chars=paste(unlist(coeff_chars),collapse=','),
                      coeffs=paste(unlist(mod@beta),collapse=','),
                      confint_chars=paste(unlist(confintvs$group_char),collapse=','),
                      emmeans=paste(unlist(as.numeric(confintvs$emmean)),collapse=','),
                      emmeans_se=paste(unlist(as.numeric(confintvs$SE)),collapse=','),
                      confint_lwr=paste(unlist(as.numeric(confintvs$lower.CL)),collapse=','),
                      confint_upr=paste(unlist(as.numeric(confintvs$upper.CL)),collapse=','),
                      anv_chars=paste(unlist(row.names(anv_vals)),collapse=','),
                      anv_pvals=paste(unlist(anv_vals$`Pr(>Chisq)`),collapse=','),
                      anv_stats=paste(unlist(anv_vals$Chisq),collapse=','),
                      anv_dfs=paste(unlist(anv_vals$Df),collapse=','),
                      r2_m_int=cf_alt$r2m,
                      r2_c_int=cf_alt$r2c,
                      f2_m_int=cf_alt$f2m,
                      f2_c_int=cf_alt$f2c,
                      fsq_chars=paste(unlist(cohens_fsq_res$Parameter),collapse=','),
                      fsq_vals=paste(unlist(cohens_fsq_res$Cohens_f2_partial),collapse=','),
                      etasq_chars=paste(unlist(etasq_res$Parameter),collapse=','),
                      etasq_vals=paste(unlist(etasq_res$Eta2_partial),collapse=','),
                      ran_effs_char=paste(unlist(row.names(ran_effs)),collapse=','),
                      ran_effs_n=paste(unlist(ran_effs$`(Intercept)`),collapse=','))
  excel_df <- rbind(excel_df,new_row)

  #%% MODEL VALIDATION PLOTS
  cat(paste0("\n\n### model validations\n"))
  print(plot_model(mod, type = 'diag'))
  cat("\n")
  tmpt$fit.m <- predict(mod, re.form = NA)
  tmpt$fit.c <- predict(mod, re.form = NULL)

  #%% GGPLOT IMPLEMENTATION
  print(
      tmpt %>%
        ggplot() +
        geom_jitter(aes(x = speed_cond_num, y = .data[[ki]], color = subj_char), pch=20, size=10, alpha=0.2) +
        geom_line(aes(x= speed_cond_num, y=fit.c, group = subj_char),linetype = "dashed", linewidth = .5) +
        geom_line(aes(x= speed_cond_num, y=fit.m), linewidth = 2)+
        facet_wrap(~group_char) +
        ggtitle(kin_measures[kis[i]]) +
        xlab("Treadmill Speed (m/s)") +
        ylab(kin_title_chars[kis[i]]) +
        guides(group="none")
    )
}
# write.xlsx(excel_df,paste0("03312025_lme_behav_kin_",fext,"_stats.xlsx"))
```

# KIN GROUP MAIN) LME Kin ~ 1+speed+group
```{r kinspeedgroupall, echo=FALSE, message=FALSE, results="asis"}
# theme_set(theme_classic()) # This sets the default ggplot theme
#%% LOOP VARS
kis <- rep(NA,length(kin_measures))
cnt = 1;
for(j in 1:length(kin_measures)){
  kis[cnt] = j;
  cnt = cnt + 1;
}

for (i in 1:length(kis)){
  #%% SET LOOP PARAMS
  ki = kin_measures[kis[i]];

  #%% HTML TAG
  cat(paste0("\n\n## ", ki,"\n"))
  
  #%% CREATE MEAN & STD MEASURES PER CONDITION
  tmpt = dtbl;
  tmpt <- tmpt %>%
    group_by(subj_char,cond_char,speed_n,model_n,group_char) %>%
    summarise_all(list("mean"))
  
  #%% SUBSET BY CLUSTER
  #-- remove NAN cases
  tmpt = tmpt[complete.cases(tmpt[[ki]]),];
  #(03/26/2025) JS, this is for the COV measures

  #%% COMPUTE LME MODEL
  mod_char = paste(ki," ~ 1 + speed_cond_num + group_char + (1|subj_char)");
  mod <- lme4::lmer(str_glue(mod_char), data=tmpt);
  tbl <- mod %>%
    tbl_regression(tidy_fun = broom.mixed::tidy,
                   pvalue_fun = purrr::partial(style_pvalue, digits = 2),
                     intercept=TRUE) %>%
    add_global_p() %>%
    add_q()

  #%% PRINT TABLE
  t_out <- as_gt(tbl) %>%
    gt::tab_header(title=c("Changes in ",ki)) %>%
    gt::tab_options(table.layout = "fixed") %>%
    gt::as_raw_html()
  print(t_out)
  #-- extract fixed & random effects coeffs
  anv_vals <- car::Anova(mod,type=3)
  fix_effs <- fixef(mod)
  ran_effs <- ranef(mod)$subj_char

  #%% R-SQUARED VALUE
  # r.squaredGLMM() %>%
  #   print(str_glue("{outcome}\n R2m: {round(mod[1],4)},\tR2c: {round(mod[2],4)}\n\n"))

  #%% EFFECT SIZES
  cat(paste0("\n\n### model effect sizes\n"))
  #-- Intercept Model for Cohen's f^2
  print('intercept model\n');
  mod_char_int = paste(ki," ~ 1 + (1|subj_char)");
  tmp_mod = lme4::lmer(str_glue(mod_char_int), data=tmpt)
  cf_alt = calc_cohensf2(mod, tmp_mod)
  #-- calculate effect sizes using r-package
  anv_vals_f <- car::Anova(mod,type=3,test.statistic = "F")
  etasq_res <- effectsize::eta_squared(anv_vals_f, partial = TRUE)
  cohens_fsq_res <- effectsize::cohens_f_squared(anv_vals_f, partial = TRUE)
  #-- confidence intervals
  summ <- summary(mod);
  coeff_chars = row.names(summ$coefficients)
  confintvs <- data.frame(emmeans::emmeans(mod,spec=c('speed_cond_num','group_char'),level=0.95))
  emm = emmeans::emmeans(mod,spec=c('speed_cond_num','group_char'),level=0.95);
  bfc = emmeans::contrast(emm,adjutst="bonferroni")
  pwc = emmeans::contrast(emm,method = "pairwise")
  print(kable(anv_vals));
  print(kable(data.frame(bfc)));
  print(kable(data.frame(pwc)));
  print(kable(confintvs));
  
  #%% EXCEL PRINTS
  new_row = data.frame(cluster_num=0,
                      group_char=c('all'),
                      model_char=c('speed_group_all'),
                      kinematic_char=c(ki),
                      freq_band_char=c('none'),
                      mod_num_obs=nrow(tmpt),
                      coeff_chars=paste(unlist(coeff_chars),collapse=','),
                      coeffs=paste(unlist(mod@beta),collapse=','),
                      confint_chars=paste(unlist(confintvs$group_char),collapse=','),
                      emmeans=paste(unlist(as.numeric(confintvs$emmean)),collapse=','),
                      emmeans_se=paste(unlist(as.numeric(confintvs$SE)),collapse=','),
                      confint_lwr=paste(unlist(as.numeric(confintvs$lower.CL)),collapse=','),
                      confint_upr=paste(unlist(as.numeric(confintvs$upper.CL)),collapse=','),
                      anv_chars=paste(unlist(row.names(anv_vals)),collapse=','),
                      anv_pvals=paste(unlist(anv_vals$`Pr(>Chisq)`),collapse=','),
                      anv_stats=paste(unlist(anv_vals$Chisq),collapse=','),
                      anv_dfs=paste(unlist(anv_vals$Df),collapse=','),
                      r2_m_int=cf_alt$r2m,
                      r2_c_int=cf_alt$r2c,
                      f2_m_int=cf_alt$f2m,
                      f2_c_int=cf_alt$f2c,
                      fsq_chars=paste(unlist(cohens_fsq_res$Parameter),collapse=','),
                      fsq_vals=paste(unlist(cohens_fsq_res$Cohens_f2_partial),collapse=','),
                      etasq_chars=paste(unlist(etasq_res$Parameter),collapse=','),
                      etasq_vals=paste(unlist(etasq_res$Eta2_partial),collapse=','),
                      ran_effs_char=paste(unlist(row.names(ran_effs)),collapse=','),
                      ran_effs_n=paste(unlist(ran_effs$`(Intercept)`),collapse=','))
  excel_df <- rbind(excel_df,new_row)

  #%% MODEL VALIDATION PLOTS
  cat(paste0("\n\n### model validations\n"))
  print(plot_model(mod, type = 'diag'))
  cat("\n")
  tmpt$fit.m <- predict(mod, re.form = NA)
  tmpt$fit.c <- predict(mod, re.form = NULL)

  #%% SCATTER3D IMPLEMENTATION
  print(
      tmpt %>%
        ggplot() +
        geom_jitter(aes(x = speed_cond_num, y = .data[[ki]], color = subj_char), pch=20, size=10, alpha=0.2) +
        geom_line(aes(x= speed_cond_num, y=fit.c, group = subj_char),linetype = "dashed", linewidth = .5) +
        geom_line(aes(x= speed_cond_num, y=fit.m), linewidth = 2)+
        facet_wrap(~group_char) +
        ggtitle(kin_measures[kis[i]]) +
        xlab("Treadmill Speed (m/s)") +
        ylab(kin_title_chars[kis[i]]) +
        guides(group="none")
    )
}
#%% SAVE STATS
write.xlsx(excel_df,paste0("03312025_lme_behav_kin_",fext,"_stats.xlsx"))
```


# MODERATION ALL) LME EEG ~ 1+speed+kin+speed:kin
```{r eegspeedkininterall, echo=FALSE, message=FALSE, results="asis"}
theme_set(theme_classic()) # This sets the default ggplot theme
#%% LOOP VARS
cis <- rep(NA,length(clusters)*length(kin_measures)*length(eeg_measures))
kis <- rep(NA,length(clusters)*length(kin_measures)*length(eeg_measures))
eis <- rep(NA,length(clusters)*length(kin_measures)*length(eeg_measures))
cnt = 1;
for (i in 1:length(clusters)) {
  for(j in 1:length(kin_measures)){
    for(k in 1:length(eeg_measures)){
      cis[cnt] = i;
      kis[cnt] = j;
      eis[cnt] = k;
      cnt = cnt + 1;
    }
  }
}

for (i in 1:length(cis)){
  #%% SET LOOP PARAMS
  ci = clusters[cis[i]];
  ki = kin_measures[kis[i]];
  ei = eeg_measures[eis[i]];

  #%% HTML TAG
  cat(paste0("\n\n## ", ci,',', ki,',',ei,"\n"))

  #%% SUBSET BY CLUSTER
  tmpt <- filter_at(dtbl,vars('cluster_n'), any_vars(. %in% ci));

  #%% REMOVE KIN_MEASURES < 0.005 & THAT ARE GREATER THAN OR LESS THAN 3STD FROM MEAN
  #- remove NAN cases
  tmpt = tmpt[complete.cases(tmpt[[ki]]),];

  #%% COMPUTE LME MODEL
  mod_char = paste(ei," ~ 1 + speed_cond_num + ",ki," + speed_cond_num:",ki," + (1|subj_char)");
  mod <- lme4::lmer(str_glue(mod_char), data=tmpt);
  tbl <- mod %>%
    tbl_regression(tidy_fun = broom.mixed::tidy,
                   pvalue_fun = purrr::partial(style_pvalue, digits = 2),
                     intercept=TRUE) %>%
    add_global_p() %>%
    add_q()

  #%% PRINT TABLE
  t_out <- as_gt(tbl) %>%
    gt::tab_header(title=c("Changes in ",ki,"for Cluster: ",ci)) %>%
    gt::tab_options(table.layout = "fixed") %>%
    gt::as_raw_html()
  print(t_out)
  
  #-- extract fixed & random effects coeffs
  anv_vals <- car::Anova(mod,type=3)
  fix_effs <- fixef(mod)
  ran_effs <- ranef(mod)$subj_char

  #%% R-SQUARED VALUE
  # r.squaredGLMM() %>%
  #   print(str_glue("{outcome}\n R2m: {round(mod[1],4)},\tR2c: {round(mod[2],4)}\n\n"))

  #%% EFFECT SIZES
  cat(paste0("\n\n### model effect sizes\n"))
  #-- Intercept Model for Cohen's f^2
  print('intercept model\n');
  mod_char_int = paste(ei," ~ 1 + (1|subj_char)");
  tmp_mod = lme4::lmer(str_glue(mod_char_int), data=tmpt)
  cf_alt = calc_cohensf2(mod, tmp_mod)
  #-- calculate effect sizes using r-package
  anv_vals_f <- car::Anova(mod,type=3,test.statistic = "F")
  etasq_res <- effectsize::eta_squared(anv_vals_f, partial = TRUE)
  cohens_fsq_res <- effectsize::cohens_f_squared(anv_vals_f, partial = TRUE)
  #-- confidence intervals
  summ <- summary(mod);
  coeff_chars = row.names(summ$coefficients)
  confintvs <- data.frame(emmeans::emmeans(mod,spec=c('speed_cond_num',ki),level=0.95))
  emm = emmeans::emmeans(mod,spec=c('speed_cond_num',ki),level=0.95);
  # bfc = emmeans::contrast(emm,adjutst="bonferroni")
  # pwc = emmeans::contrast(emm,method = "pairwise")
  print(kable(anv_vals));
  print(kable(confintvs));
  
  #%% EXCEL PRINTS
  new_row = data.frame(cluster_num=ci,
                      group_char=c('all'),
                      model_char=c('speed_eeg_kin_intact'),
                      kinematic_char=c(ki),
                      freq_band_char=c(ei),
                      mod_num_obs=nrow(tmpt),
                      coeff_chars=paste(unlist(coeff_chars),collapse=','),
                      coeffs=paste(unlist(mod@beta),collapse=','),
                      confint_chars=c('none'),
                      emmeans=paste(unlist(as.numeric(confintvs$emmean)),collapse=','),
                      emmeans_se=paste(unlist(as.numeric(confintvs$SE)),collapse=','),
                      confint_lwr=paste(unlist(as.numeric(confintvs$lower.CL)),collapse=','),
                      confint_upr=paste(unlist(as.numeric(confintvs$upper.CL)),collapse=','),
                      anv_chars=paste(unlist(row.names(anv_vals)),collapse=','),
                      anv_pvals=paste(unlist(anv_vals$`Pr(>Chisq)`),collapse=','),
                      anv_stats=paste(unlist(anv_vals$Chisq),collapse=','),
                      anv_dfs=paste(unlist(anv_vals$Df),collapse=','),
                      r2_m_int=cf_alt$r2m,
                      r2_c_int=cf_alt$r2c,
                      f2_m_int=cf_alt$f2m,
                      f2_c_int=cf_alt$f2c,
                      fsq_chars=paste(unlist(cohens_fsq_res$Parameter),collapse=','),
                      fsq_vals=paste(unlist(cohens_fsq_res$Cohens_f2_partial),collapse=','),
                      etasq_chars=paste(unlist(etasq_res$Parameter),collapse=','),
                      etasq_vals=paste(unlist(etasq_res$Eta2_partial),collapse=','),
                      ran_effs_char=paste(unlist(row.names(ran_effs)),collapse=','),
                      ran_effs_n=paste(unlist(ran_effs$`(Intercept)`),collapse=','))
  excel_df <- rbind(excel_df,new_row)

  #%% MODEL VALIDATION PLOTS
  cat(paste0("\n\n### model validations\n"))
  print(plot_model(mod, type = 'diag'))
  cat("\n")

  #%% SCATTER3D IMPLEMENTATION
  cat(paste0("\n\n### plot\n"))
  xc = "speed_cond_num";
  yc = ki;
  intc = paste0(xc,":",yc)
  #- plot
  pch_n = 1;
  conds = rev(unique(tmpt[[xc]]))
  for(i in 1:length(conds)){
    ts <- filter_at(tmpt,vars(xc),all_vars(. == conds[i]))
    if(i == 1){
      scatter <- scatterplot3d(ts[[yc]], ts[[xc]], ts[[ei]],
        main = paste0(eeg_title_chars[eis[i]],"plot"),
        xlab = kin_title_chars[kis[i]],
        ylab = "Speed (m/s)",
        zlab = eeg_title_chars[eis[i]],
        xlim = c(min(tmpt[[yc]]),max(tmpt[[yc]])),
        ylim = c(min(tmpt[[xc]]),max(tmpt[[xc]])),
        zlim = c(min(tmpt[[ei]]),max(tmpt[[ei]])),
        pch = pch_n,
        color = color_pal_subj[i],
        angle = 30) # adjust the viewing angle
    } else {
    scatter$points3d(ts[[yc]], ts[[xc]], ts[[ei]] ,
        main = paste0(eeg_title_chars[eis[i]],"plot"),
        col = color_pal_subj[i],
        pch=pch_n)
    }
  }
  a <- fix_effs[xc]
  b <- fix_effs[yc]
  c <- fix_effs[intc]
  d <- fix_effs["(Intercept)"]
  # Create the plane's z-values using the equation of the plane
  plane_z <- function(y,x){a*x+b*y+c*x*y+d}
  scatter$contour3d(plane_z,y.count=4,
                    x.count=4,
                    y.resolution=10,
                    x.resolution=10,
                    lty="24",
                    type="l")

}
# write.xlsx(excel_df,"01302025_lme_eeg_kin_raw_slidingavgb5.xlsx")
# write.xlsx(excel_df,paste0("01302025_lme_eeg_kin_",fext,"_stats.xlsx"))
write.xlsx(excel_df,paste0("03312025_lme_eeg_kin_",fext,"_stats.xlsx"))
```
M:/jsalminen/GitHub/MIND_IN_MOTION_PRJ/MindInMotion_YoungerOlderAdult_KinEEGCorrs/src/step_to_step_anlz/__archive/ff_eeg_psd_speed_all_plots.m